Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-26 paper/main.tex

For the experiments we used the version of \texttt{telatko} build with
Spot library version 2.10.4 and Z3 version 4.8.15. The experiments
have been run on a computer with Intel® Core™ i7-8700 processor and 32
GB of memory running Ubuntu 20.04.4. We used the tool
\texttt{autcross} of the Spot library to get the statistics of the
reduced automata and the running times.

Table~\ref{tab:cumm-data} shows the cummulative numbers of marks in
the input automata sets and after each reduction, together with the
reduction ratio and total time spent by the considered reduction. The
column \textit{solver timeout} shows the number of automata for which
the last query to QBF solver did not finished within the 30 seconds
limit. The timeout of the last QBF query implies that the automaton
may be potentially further reduced by the reduction with a longer time
limit.

\begin{table}[t]
  \caption{The cummulative numbers of acceptance marks before and
    after reduction for various reductions and automata sets. The
    column \emph{reduction} shows the cummulative percentage of saved
    acceptance marks and \emph{time} reports the cummulative reduction
    time.
%\textit{X/Y solved aut.} means that out of
%\textit{Y} successfully translated LTL formulas, every run of \telatko ended
%within 120 seconds time limit on \textit{X} automata. We sum up the acceptance
%marks only on these automata.
The column \textit{solver timeout} indicates the number of instances
when the last call to the QBF solver timed out.  }
\label{tab:cumm-data}
\centering
\setlength{\tabcolsep}{10pt}
\input{table-data.tex}
\end{table}

>>>>

For the experiments, we used the version of \texttt{telatko} build with
Spot library version 2.10.4 and Z3 version 4.8.15. The experiments
have been run on a computer with Intel® Core™ i7-8700 processor and 32
GB of memory running Ubuntu 20.04.4. We used the tool
\texttt{autcross} of the Spot library to get the statistics of the
reduced automata and the running times.

Table~\ref{tab:cumm-data} shows the cumulative numbers of marks in
the input automata sets and after each reduction, together with the
reduction ratio and total time spent by the considered reduction. The
column \textit{solver timeout} shows the number of automata for which
the last query to QBF solver did not finished within the 30 seconds
limit. The timeout of the last QBF query implies that the automaton
may be potentially further reduced by the reduction with a longer time
limit.

\begin{table}[t]
  \caption{The cumulative numbers of acceptance marks before and after
    reduction for various reductions and automata sets. The column
    \emph{reduction} shows the cumulative percentage of saved
    acceptance marks and \emph{time} reports the cumulative reduction
    time. The column \textit{solver timeout} indicates the number of
    instances when the last call to the QBF solver timed out.  }
\label{tab:cumm-data}
\centering
\setlength{\tabcolsep}{10pt}
\input{table-data.tex}
\end{table}
